Lightness constancy under fixed geometry

### 2017-12-19 Draft1/draft1.tex
Today’s editing

\section*{Methods} \label{Methods}
\subsection{Image database} \label{method:VirtualWorld}
We call our image generation software Virtual world color constancy (VWCC). The details of the software are provided in the supplementary information section. To generate an image, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects in VWCC. The target object and the light source are inserted in the 3D scene. Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene used in our analysis. The green sphere in the middle is the target object. The light source is not in the camera field of view. Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene. For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value. Now we render a $320\times 240$ pixel$^2$ 2d multispectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}. For each of the three case, we generate hundreds of such scenes and corresponding multispectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below). We crop a 51x51 pixel$^2$ part of the multispectral image containing the target object for further analysis (\ref{fig:croppedImage}). Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this work.

@@

\subsection{Model of Visual System} \label{method:Isetbio}
We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox. Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics. We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina. The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m. The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1. The response of the cones are measured as the number of isomerizations in the cone segment ({\it over what time ??}). The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones. Further, to get the response of each cone class at each position on the retinal mosaic, we interpolate the response of each cone class. Thus we get a $51 \times 51$ cone response image for each cone class.

@@

\section{Discussion} \label{Discussion}
\section{Supplementary Information}
\subsection{Virtual World Color Constancy}
The light that reflects off an object and reaches our eyes depends on many factors. These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer. In natural scenes, these spectral and geometrical factors vary considerably. To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors. We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene. Under natural conditions it is difficult to control and quantify every such parameter in a scene. Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.

The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}). The base scene is a 3D model that defines a rendering space.  It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position. VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses. We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly. We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene. Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).  The overall scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness. If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes. As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library. Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
        \caption{Indoor-plant}
        \label{fig:baseSceneIndoorPlant}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
        \caption{Warehouse}
        \label{fig:baseSceneWarehouse}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
        \caption{Checkerboard}
        \label{fig:baseSceneCheckerBoard}
    \end{subfigure}
    \caption{Example of base scenes.}\label{fig:baseScenes}
\end{figure}

VWCC provides an option for inserting 3D objects and lights sources into the base scene. Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted in the library base scene. The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from materials made available on the Internet. The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
        \caption{Xylophone}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
        \caption{Ring toy}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
        \caption{Champagne Bottle}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{Base scenes with inserted objects.}\label{fig:libraryWithTarget}
\end{figure}

The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data. As with the base scene library, the object may be drawn at random from the VWCC object library.  Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.

Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene. We also assign the illuminant spectral power distribution to each light source in the scene. Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance. As with object position, these may be specified programatically. In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.

[GOT TO HERE.  DHB.]
% Figure11
\begin{figure}
\centering
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
        \caption{Target spectra}
        \label{fig:targetVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
        \caption{Background spectra}
        \label{fig:backGroundVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
        \caption{Illumination spectra}
        \label{fig:illuminationVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
        \caption{Target position}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
        \caption{Target Size/Orientation}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \caption{{\bf Transformations of the scene:} (a-c) Spectral Transformations. (d-e) Geometrical transformations.}\label{fig:spectralTransformations}
\end{figure}

One of the inserted objects is chosen as the target object in the scene. A camera is inserted at a user specified position and pointed at the target object. We ensure that the target object is not completely occluded by other objects in the line of sight of the camera. A predefined surface reflectance spectrum is assigned to the target object. This target surface reflectance also sets the label for the virtual scene image. The image label is defined as the perceived lightness of a uniform object with the surface reflectance same as that of the the target object when viewed under uniform standard daylight spectrum D65. The scene is rendered using the Mitsuba rendering package. The renderer produces 2D multispectral images of the scene at specified wavelengths. Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.

For the images used in this work, we have used the ``{\it Library}'' base scene from the VWCC  as the and the ``{\it Big Ball}'' object as the target object. We also inserted a spherical light source with the same ``{\it Big Ball}'' shape. The position, and size of the inserted object, light source and the camera was held fixed for all the images analyzed in this work, i.e., the images were identical in their geometry. Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene. The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}). 2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$. A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.

\subsection{Generating Spectrum for VWCC}
\subsubsection{Illumination Spectrum}
The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset. First, we approximate the spectra in the dataset using principle component analysis (PCA). We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues. Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.

>>>>

\section*{Methods} \label{Methods}
\subsection{Overview}

There are four key parts to our methods.  The first is how we generate a labelled set of training data for our supervised learning algorithms.  The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.  The third is the details of the supervised learning methods we apply to the labelled training data.  And the fourth is how we evaluate the performance of the algorithms.  We describe each of these in the sections below.

\subsection{Labelled image database} \label{method:VirtualWorld}

\subsubsection{Virtual naturalistic scenes}

The light that reflects off an object and reaches our eyes depends on many factors. These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer. In natural scenes, these spectral and geometrical factors vary considerably. To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors. We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene. Under natural conditions it is difficult to control and quantify every such parameter in a scene. Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.

The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}). The base scene is a 3D model that defines a rendering space.  It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position. VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses. We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly. We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene. Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).  The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness. If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes. As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library. Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
        \caption{Indoor-plant}
        \label{fig:baseSceneIndoorPlant}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
        \caption{Warehouse}
        \label{fig:baseSceneWarehouse}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
        \caption{Checkerboard}
        \label{fig:baseSceneCheckerBoard}
    \end{subfigure}
    \caption{{Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.  The reflectance spectra of the distinct surfaces in each scene has been assigned randomly (see below) using the VWCC software.  The light source spectra were also assigned randomly to the default light source for each scene. [CHECK THAT THIS IS CORRET] }\label{fig:baseScenes}
\end{figure}

VWCC provides an option for inserting 3D objects and lights sources into the base scene. Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene. The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet. The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
        \caption{Xylophone}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
        \caption{Ring toy}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
        \caption{Champagne Bottle}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object. The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.  In the figure panels, the full rendered image is cropped so that the inserted object is more visually salient. We use this capability of our software pipeline to insert target objects into scenes.}\label{fig:libraryWithTarget}
\end{figure}

The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data. Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.

Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene. We also assign an illuminant spectral power distribution to each light source in the scene. Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance. As with object position, these may be specified programatically. In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.

% Figure11
\begin{figure}
\centering
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
        \caption{Target spectra}
        \label{fig:targetVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
        \caption{Background spectra}
        \label{fig:backGroundVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
        \caption{Illumination spectra}
        \label{fig:illuminationVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
        \caption{Target position}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
        \caption{Target Size/Orientation}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \caption{{\bf Transformations of the scene.} Each column illustrates transformations of a scene that are under software control. (a-c) Spectral Transformations. (d-e) Geometrical transformations. EXPAND OUT AND SAY WHAT EACH COLUMN IS, INDIVIDUALLY}\label{fig:spectralTransformations}
\end{figure}

In the present work, we insert one target object and one additional light source into a fixed base scene, and vary reflectance and illuminant spectra. We then insert a camera for rendering at a user specified position and point this camera at the target object. We ensure that a N by N pixel [CHECK ACTUAL SIZE] region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera. For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance. The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.

We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.

For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object. We also inserted a spherical light source with the same ``{\it Big Ball}'' shape. The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary. Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene. The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}). 2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$. A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.

[GOT TO HERE]
\subsubsection{Illumination Spectra}
The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset. First, we approximate the spectra in the dataset using principle component analysis (PCA). We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues. Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.

% NEED TO DECIDE PRECISELY WHERE TO USE THIS PROSE AND  FIGURE
%Figure~\ref{sceneWithCroppedImage} illustrates the steps in this process for one scene.  We start with how we generate a single labeled set of cone responses
%We call our image generation software Virtual world color constancy (VWCC). The details of the software are provided in the supplementary information section. To generate an image, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects in VWCC. The target object and the light source are inserted in the 3D scene. Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene used in our analysis. The green sphere in the middle is the target object. The light source is not in the camera field of view. Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene. For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value. Now we render a $320\times 240$ pixel$^2$ 2d multispectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}. For each of the three case, we generate hundreds of such scenes and corresponding multispectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below). We crop a 51x51 pixel$^2$ part of the multispectral image containing the target object for further analysis (\ref{fig:croppedImage}). Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this work.

@@

\subsection{Model of Visual System} \label{method:Isetbio}

Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.

We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox. Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics. We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina. The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m. The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1. The response of the cones are measured as the number of isomerizations in the cone segment ({\it over what time ??}). The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones. Further, to get the response of each cone class at each position on the retinal mosaic, we interpolate the response of each cone class. Thus we get a $51 \times 51$ cone response image for each cone class.

@@

\section{Discussion} \label{Discussion}
\section{Supplementary Information}
